Forecasting short-term hourly Emergency Departement arrivals

### 2021-11-09 paper/paper.Rmd
Minor changes
Comments for the figures

# Experimental design {#design}

## Preliminary analysis {#data}

@@

\begin{equation}
     <!-- \text{Skill} = \frac{M_\text{ref} - M}{M_\text{ref} - M_\text{perf}} (\#eq:skillscore) -->
     \mathrm{Skill} = \frac{M_\mathrm{ref} - M}{M_\mathrm{ref}} (\#eq:skillscore)
\end{equation}
where $M$ is the metric's value for the method being considered, $M_\mathrm{ref}$ is the metric's value for a reference method. The skill score showas by how many percent the reference approach is worse than the one under consideration.
<!-- and $M_\mathrm{perf}$ is the metrics value for the `perfect' method, which is zero in the case of RMSE and Pinball. -->
We will use bootstrap re-sampling of skill scores to determine if apparent differences in forecast performance (i.e. positive or negative skill) are significantly different from zero [@Efron1981Bootstrap]. Here we use the best performing simple benchmark, Climatology (explained in Subsection \@ref(climatology)), as the reference model, and employ a block-boostrap with blocks of length 24h in order to account for temporal correlations of the underlying data [we need a reference here].

@@

<!-- IS: This plot is difficult to read. Do we need it at all? -->
```{r lead-time-rel, fig.cap= "Pinball values over different forecast horizons.", fig.align='center',out.width= "90%"}
```

@@

```{r tab-results, out.width= "50%"}
results_table <- read_rds("results_table.rds")
knitr::kable(results_table, booktabs = T, 
             linesep = "",caption = "Summary of studies in hourly emergency care forecasting") %>% kableExtra::kable_styling(latex_options = c("hold_position"), font_size =11)
```

@@

<!-- IS: Round values in the table to 3 or 4 digits -->
```{r Skill-rel2bench-reduced, fig.cap= "Skill score ...", fig.align='center',out.width= "70%"}

>>>>

# Preliminary analysis {#data}

@@

\begin{equation}
     <!-- \text{Skill} = \frac{M_\text{ref} - M}{M_\text{ref} - M_\text{perf}} (\#eq:skillscore) -->
     \mathrm{Skill} = \frac{M_\mathrm{ref} - M}{M_\mathrm{ref}} (\#eq:skillscore)
\end{equation}
where $M$ is the metric's value for the method being considered, $M_\mathrm{ref}$ is the metric's value for a reference method. The skill score show us by how many percent the reference approach is worse than the one under consideration.
<!-- and $M_\mathrm{perf}$ is the metrics value for the `perfect' method, which is zero in the case of RMSE and Pinball. -->
We will use bootstrap re-sampling of skill scores to determine if apparent differences in forecast performance (i.e. positive or negative skill) are significantly different from zero [@Efron1981Bootstrap]. Here we use the best performing simple benchmark, Climatology (explained in Subsection \@ref(climatology)), as the reference model, and employ a block-boostrap with blocks of length 24h in order to account for temporal correlations of the underlying data [we need a reference here].

@@

<!-- IS: This plot is difficult to read. Do we need it at all? -->
<!-- {r lead-time-rel, fig.cap= "Pinball values over different forecast horizons.", fig.align='center',out.width= "90%"} -->

@@

<!-- IS: round values to 3 or 4 decimals -->
```{r tab-results, out.width= "50%"}
results_table <- read_rds("results_table.rds")
knitr::kable(results_table, booktabs = T, 
             linesep = "",caption = "Summary of studies in hourly emergency care forecasting") %>% kableExtra::kable_styling(latex_options = c("hold_position"), font_size =11)
```

@@

```{r Skill-rel2bench-reduced, fig.cap= "Skill score ...", fig.align='center',out.width= "70%"}
